---
title: "Your A4 Report Title (TODO: Revise title)"
author: "Daphne He"
date: "Autumn 2022"
output: html_document
---

```{r echo=FALSE, eval=TRUE, message=FALSE}
source("../source/a4-helpers.R")
source("../source/analysis.R")
```

## Abstract 
[TODO: Include a short abstract (about 50 words)]

# Test (TODO: Remove before submission!!)
```{r echo=FALSE}
q1_string <- test_query1()
num <- 5
```
As you know, this is a markdown report. The [R Markdown Cheatsheet](https://www.rstudio.com/wp-content/uploads/2015/02/rmarkdown-cheatsheet.pdf) is **useful!**

* Here's a test of a dynamic variable. Say **"`r q1_string`!!!** 
* Here's another test. A vector
* Another bullet point
of numbers: `r test_query2(num)`.

Recall that _{r echo=TRUE}_ can be used to display the code, 
which is very useful when developing and debugging a report. Here's an example: 

```{r echo=TRUE}
num <- 5
sum <- sum(test_query2(num))
print(sum)
```

## Introduction (Section 1)
The American jail and prison system have systemically oppressed Black people.

```{r echo=FALSE}
black_2018 <- avg_black_incarcerated_2018()
black_2000 <- avg_black_incarcerated_2000()
white_2018 <- avg_white_incarcerated_2018()
max_black <- black_max_incarcerated()
```

## Data Summary (Section 2)
The Black incarcerated population count average for ages 15-64 in 2018 was `r black_2018`.
The Black incarcerated population count average for ages 15-64 in 2000 was `r black_2000`.
The White incarcerated population count average for ages 15-64 in 2018 was `r white_2018`.
Incarceration of Black people ages 15-64 was highest in `r max_black`.


## Growth of the U.S. Prison Population (Section 3)
```{r echo=FALSE}
plot(plot_jail_pop_for_us())
```

[INSERT CHART CAPTION HERE]

[INSERT SUMMARY PARAGRAPH HERE (ADD A QUESTION)]


## Growth of Prison Population by State (Section 4)

```{r echo=FALSE}
plot_jail_pop_by_states(c("WA", "OR", "CA"))
```

[TODO ... other sections ... See Canvas for details]

_All the very best with your work!_

